---
title: "Herper QuickStart"
author: 
- Matt Paul
- Bioinformatics Resource Center - Rockefeller University
- "mpaul@rockefeller.edu"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### The Herper package is a simple toolset to install and manage Conda packages and environments from R.
 
 ______
 
 
## Installation

Use the `BiocManager` package to download and install the package from our Github repository:

```{r getPackage, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("https://github.com/RockefellerUniversity/CondaSysReqs")
```

Once installed, load it into your R session:

```{r, warning=FALSE, message=FALSE}
library(CondaSysReqs)
```


## Install Conda packages with **install_CondaTools**. 

The **install_CondaTools()** function allows the user to specify required Conda software and the desired environment to install into.

Miniconda is installed as part of the process (by default into the r-reticulate's default Conda location). If you already have Miniconda installed you specify the path with the *pathToMiniConda* parameter.


```{r, echo=T, eval=F}
install_CondaTools("salmon", "myCondaToolSet")
```

```{r, echo=F, eval=T, warning=FALSE, message=FALSE}
install_CondaTools("salmon", "myCondaToolSet", pathToMiniConda="/tmp/")
```

## Install R package dependencies **install_CondaTools**. 


```{r}
#install_CondaTools("salmon", "myCondaToolSet")
```

## Acknowledgements
The Herper package was developed by Matt Paul, Tom Carroll and Doug Barrows. Thank you to Ji-Dung Luo and Wei Wang for testing/vignette review/critical feedback and Ziwei Liang for their support.

## Session Information

```{r}
devtools::session_info()
```

