---
title: "Herper Quick Start Guide"
author: "Matt Paul - mpaul@rockefeller.edu"
date: "`r format(Sys.Date(), '%m/%d/%Y')`"
package: CondaSysReqs
output:
 BiocStyle::html_document:
  number_sections: yes
  toc: true
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\usepackage[utf8]{inputenc}
---

```{r setup, echo=FALSE, results="hide", include = FALSE}
knitr::opts_chunk$set(tidy=FALSE, cache=FALSE,
                      #dev="png",
                      message=FALSE, error=FALSE, warning=TRUE)
options(width=100)
```

<br>



The Herper package is a simple toolset to install and manage Conda packages and environments from R.
 
______
 
 
## Installation

Use the `BiocManager` package to download and install the package from our Github repository:

```{r getPackage, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("https://github.com/RockefellerUniversity/CondaSysReqs")
```

Once installed, load it into your R session:

```{r}
library(CondaSysReqs)
```


## Install Conda packages with **install_CondaTools**. 

The **install_CondaTools()** function allows the user to specify required Conda software and the desired environment to install into.

Miniconda is installed as part of the process (by default into the r-reticulate's default Conda location). If you already have Miniconda installed (or want to control the location of miniconda installation), you can specify the path with the *pathToMiniConda* parameter.


```{r install_Condatools, echo=T, eval=F}
myMiniconda <- file.path(tempdir(),"Test")
install_CondaTools("salmon", "herper", pathToMiniConda = myMiniconda)
```

## Install R package dependencies with **install_CondaSysReqs**. 
The **install_CondaSysReqs** checks the System Requirements for the specified R package, and uses Conda to install this software.

```{r install_CondaSysReqs, eval=F}
install_CondaSysReqs("basecallQC")

```

## Acknowledgements
The Herper package was developed by Matt Paul, Tom Carroll and Doug Barrows in the Bioinformatics Resource Center at Rockefeller University. Thank you to Ji-Dung Luo and Wei Wang for testing/vignette review/critical feedback and Ziwei Liang for their support.

## Session Information

```{r sessionInfo}
sessionInfo()
```

